Supply diversity

### 2023-03-31 ms_figures.Rmd

```{r fig4a_old, eval = FALSE}
fig4a_data <- read.csv(file.path(datadir, "fig4a_data.csv"))

fig4a <- fig4a_data %>%
  ggplot(aes(x = year, y = shannon, color = source)) +
  geom_line() +
  scale_color_manual(values = c(c("#F37542", "#0F2D59"))) +
  labs(x = "", y = "Shannon index", color = "") +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~region)

fig4a
```

```{r fig4a}
diversity <- read.csv("/Volumes/jgephart/ARTIS/Outputs/diversity/max_per_capita_100kg/diversity.csv")
fig4a <- diversity %>% 
  filter(year == 2019) %>%
  select(iso3c, region, "Production" = "shannon_prod", "Imports" = "shannon_imports", "Exports" = "shannon_exports") %>% 
  pivot_longer(Production:Exports, names_to = "shannon_var", values_to = "shannon_index") %>%
  mutate(shannon_var = factor(shannon_var, levels = c("Production", "Imports", "Exports"))) %>%
  ggplot(aes(x = shannon_var, y = shannon_index, fill = shannon_var)) +
  geom_violin() + 
  geom_point(alpha = 0.5) +
  scale_fill_manual(values = c(habitat_source_colors[1], habitat_source_colors[3], habitat_source_colors[4])) +
  labs(x = "", y = "Shannon index", fill = "") +
  facet_wrap(~region, nrow=1) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank(),
        text = element_text(size = 18)
        )

fig4a
```

```{r fig4b_old, eval=FALSE}
fig4b_data <- read.csv(file.path(datadir, "fig4b_data.csv"))

fig4b <- fig4b_data %>%
  ggplot(aes(x = shannon_domestic, y = shannon_foreign, color = region)) +
    geom_point(alpha = 0.7) +
    geom_abline(slope = 1, intercept = 0) +
  scale_color_manual(values = region_colors) +
  labs(x = "Domestic supply diversity", 
       y = "Foreign supply diversity",
       color = "") +
    theme_minimal()

fig4b
```

```{r fig4b}
fig4b <- diversity %>% 
  filter(year == 2019) %>%
  select(iso3c, region, "Domestic" = "shannon_domestic", "Foreign" = "shannon_foreign") %>% 
  pivot_longer(Domestic:Foreign, names_to = "shannon_var", values_to = "shannon_index") %>%
  mutate(shannon_var = factor(shannon_var, levels = c("Domestic", "Foreign"))) %>%
  ggplot(aes(x = shannon_var, y = shannon_index, fill = shannon_var)) +
  geom_violin() + 
  geom_point(alpha = 0.5) +
  scale_fill_manual(values = c(habitat_source_colors[2], habitat_source_colors[4])) +
  labs(x = "", y = "Shannon index", fill = "") +
  facet_wrap(~region, nrow=1) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank(),
        text = element_text(size = 18))

fig4b
```

```{r fig4c}
fig4c_data <- read.csv(file.path(datadir, "fig4c_data.csv"))

fig4c <- fig4c_data %>%
  # total supply greater than 1 tonne (FIXIT update manuscript caption)
  filter(supply > 1) %>%
  ggplot(aes(x = imports/1000000, y = shannon_supply, color = region)) +
  geom_point(alpha = 0.7) +
  scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x))) +
  annotation_logticks(sides = "b") +
  scale_color_manual(values = region_colors) +
  theme_minimal() +
  labs(x = "Total imports (million t, live weight)",
       y = "Supply diversity",
       color = "") +
  theme(
    text = element_text(size = 18)
  )

#

fig4c
```
```{r fig4d}
fig4d_data <- read.csv(file.path(datadir, "fig4c_data.csv"))

fig4d <- fig4d_data %>%
  # total supply greater than 1 tonne (FIXIT update manuscript caption)
  filter(supply > 1) %>%
  ggplot(aes(x = exports/1000000, y = shannon_supply, color = region)) +
  geom_point(alpha = 0.7) +
  scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x))) +
  annotation_logticks(sides = "b") +
  scale_color_manual(values = region_colors) +
  theme_minimal() +
  labs(x = "Total exports (million t, live weight)",
       y = "Supply diversity",
       color = "") +
  theme(
    text = element_text(size = 18)
  )

#

fig4d
```

```{r fig4, fig.height = 5, fig.width = 7}
fig4 <- ggarrange(
  ggarrange(
    fig4a, fig4b,
    ncol = 1,
    nrow = 2,
    labels = c("a", "b")
  ),
  ggarrange(
    fig4c, fig4d,
    ncol = 1,
    nrow = 2,
    common.legend = TRUE,
    legend = "bottom",
    labels = c("c", "d")
  ),
  nrow = 1, ncol = 2,
  widths = c(1, 0.5)
)

fig4

ggsave(file.path(outdir, "fig4.png"))
```

```{r fig4_old, fig.height = 7, fig.width = 7, eval = FALSE}
fig4 <- ggarrange(fig4a,
                  fig4b,
          ggarrange(fig4d,
                    fig4e,
                    nrow = 1,
                    common.legend = TRUE, 
                    legend = "bottom",
                    labels = c("c", "d")),
          nrow = 3,
          labels = c("a", "b", "")
          )

fig4

ggsave(file.path(outdir, "fig4.png"))
```

@@

ggsave("dom_source_2019_overview.png")
```

@@

ggsave("foreign_exports_2019_by_source.png")
```

>>>>

@@

ggsave(file.path(outdir, "dom_source_2019_overview.png"))
```

@@

ggsave(file.path(outdir, "foreign_exports_2019_by_source.png"))
```

### 2023-03-31 supply_diversity.Rmd

```{r fig4a_old}
fig4a_data <- read.csv(file.path(datadir, "fig4a_data.csv"))

@@

```{r fig4b_old}
fig4b_data <- read.csv(file.path(datadir, "fig4b_data.csv"))

@@

```{r fig4c, eval=FALSE}
fig4c_data <- read.csv(file.path(datadir, "fig4c_data.csv"))

@@

fig4c
```
```{r fig4d, eval=FALSE}
fig4d_data <- read.csv(file.path(datadir, "fig4c_data.csv"))

@@

```{r fig4, fig.height = 5, fig.width = 7, eval=FALSE}
fig4 <- ggarrange(
  ggarrange(
    fig4a, fig4b,
    ncol = 1,
    nrow = 2,
    labels = c("a", "b")
  ),
  ggarrange(
    fig4c, fig4d,
    ncol = 1,
    nrow = 2,
    common.legend = TRUE,
    legend = "bottom",
    labels = c("c", "d")
  ),
  nrow = 1, ncol = 2,
  widths = c(1, 0.5)
)

@@

```{r fig4_old, fig.height = 7, fig.width = 7, eval=FALSE}
fig4 <- ggarrange(fig4a,
                  fig4b,
          ggarrange(fig4d,
                    fig4e,
                    nrow = 1,
                    common.legend = TRUE, 
                    legend = "bottom",
                    labels = c("c", "d")),
          nrow = 3,
          labels = c("a", "b", "")
          )

>>>>

```{r fig4a_old, eval = FALSE}
fig4a_data <- read.csv(file.path(datadir, "fig4a_data.csv"))

@@

```{r fig4b_old, eval=FALSE}
fig4b_data <- read.csv(file.path(datadir, "fig4b_data.csv"))

@@

```{r fig4c}
fig4c_data <- read.csv(file.path(datadir, "fig4c_data.csv"))

@@

fig4c
```
```{r fig4d}
fig4d_data <- read.csv(file.path(datadir, "fig4c_data.csv"))

@@

```{r fig4, fig.height = 5, fig.width = 7}
fig4 <- ggarrange(
  ggarrange(
    fig4a, fig4b,
    ncol = 1,
    nrow = 2,
    labels = c("a", "b")
  ),
  ggarrange(
    fig4c, fig4d,
    ncol = 1,
    nrow = 2,
    common.legend = TRUE,
    legend = "bottom",
    labels = c("c", "d")
  ),
  nrow = 1, ncol = 2,
  widths = c(1, 0.5)
)

@@

```{r fig4_old, fig.height = 7, fig.width = 7, eval = FALSE}
fig4 <- ggarrange(fig4a,
                  fig4b,
          ggarrange(fig4d,
                    fig4e,
                    nrow = 1,
                    common.legend = TRUE, 
                    legend = "bottom",
                    labels = c("c", "d")),
          nrow = 3,
          labels = c("a", "b", "")
          )
